A simulation model of DNA methylation data

### 2015-05-05 Rmarkdown/methsim.Rmd
Fix notation

Recall that $B_{i, j}$ is the underlying _true_ methylation level at locus $i$ in sample $j$. In the context of simulating data for comparing differential methylation calling methods, we want these to be group-specific. That is, we want to specify $B_{i, j_{k}}$, where $j_{k}$ indicates that sample $j$ comes from group $k$. For non-differentially methylated loci all $k$ groups have identical $B_{i, j_{k}} = B_{i, j^{0}}$; differentially methylated loci are simulated by setting $B_{i, j_{k}} \neq B_{i, j^{k'}}$ for some $k \neq k'$.

>>>>

Recall that $B_{i, j}$ is the underlying _true_ methylation level at locus $i$ in sample $j$. In the context of simulating data for comparing differential methylation calling methods, we want these to be group-specific. That is, we want to specify $B_{i, j_{k}}$, where $j_{k}$ indicates that sample $j$ comes from group $k$. For non-differentially methylated loci all $k$ groups have identical $B_{i, j_{k}} = B_{i, j_{0}}$; differentially methylated loci are simulated by setting $B_{i, j_{k}} \neq B_{i, j_{k'}}$ for some $k \neq k'$.
